---
title: "615 Shiny HW_code"
author: "Xiaohan Shi"
date: "2024-11-16"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Question 1:  What is the difference between Hadley 1 and Hadley 2? 

Answer: Both versions demonstrate how to build a basic Shiny application and gradually optimize the logical organization of your code. Hadley_1 is a simply version that let users select a dataset (the datasets package from R) and display the summary  statistics and raw data table for that dataset. Hadley_2 is a updated version that allows users to separate UI and  server logic, making code cleaner and easier to extend


##Exercise 2.3.5

### 1
Which of textOutput() and verbatimTextOutput() should each of the following render functions be paired with?

renderPrint(summary(mtcars)): verbatimTextOutput()

renderText("Good morning!"): textOutput()

renderPrint(t.test(1:5, 2:6)): verbatimTextOutput()

renderText(str(lm(mpg ~ wt, data = mtcars))): textOutput()


### 2
```{r, eval=FALSE}
# Define UI
ui <- fluidPage(
  # Add an accessible description for the plot
  tags$p("Scatterplot of five random numbers for visually impaired users."),
  plotOutput(
    "plot", 
    width = "700px", 
    height = "300px"
  )
)

# Define Server
server <- function(input, output, session) {
  output$plot <- renderPlot({
    plot(1:5, main = "Scatterplot of Five Random Numbers", xlab = "Index", ylab = "Value")
  }, res = 96)
}

shinyApp(ui, server)
```

### 3
```{r, eval=FALSE}
ui <- fluidPage(
  DTOutput("table") 
)

server <- function(input, output, session) {
  output$table <- renderDataTable(
    mtcars,
    options = list(
      pageLength = 5,   
      searching = FALSE, 
      ordering = FALSE,  
      paging = TRUE,     
      info = FALSE      
    )
  )
}
shinyApp(ui, server)
```

### 4
```{r, eval=FALSE}
ui <- fluidPage(
  reactableOutput("table") # Use reactableOutput for Reactable tables
)

server <- function(input, output, session) {
  output$table <- renderReactable({
    reactable(
      mtcars,
      pagination = TRUE,  
      searchable = FALSE, 
      sortable = FALSE    
    )
  })
}
shinyApp(ui, server)
```

## 3.3.6

### 1
```{r, eval=FALSE}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
server <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
shinyApp(ui, server)
```

### 2
1.
```{r, eval=FALSE}
server1 <- function(input, output, session) {
  c <- reactive(input$a + input$b)
  e <- reactive(c() + input$d)
  output$f <- renderText(e())
}

Graph:

input$a ─┐
         │
input$b ─┼─> c() ──> e() ──> output$f
         │
input$d ─┘
```

2.
```{r, eval=FALSE}
server2 <- function(input, output, session) {
  x <- reactive(input$x1 + input$x2 + input$x3)
  y <- reactive(input$y1 + input$y2)
  output$z <- renderText(x() / y())
}

Graph:
input$x1 ─┐
input$x2 ─┼─> x() ──┐
input$x3 ─┘         │
                    ├─> output$z
input$y1 ─┐         │
input$y2 ─┼─> y() ──┘
```

3.
```{r, eval=FALSE}
server3 <- function(input, output, session) {
  d <- reactive(c() ^ input$d)
  a <- reactive(input$a * 10)
  c <- reactive(b() / input$c)
  b <- reactive(a() + input$b)
}

input$a ─┐
         │
         └─> a() ──┐
                   ├─> b() ──┐
input$b ───────────┘         │
                             ├─> c() ──> d()
input$c ─────────────────────┘         │
                                        │
input$d ────────────────────────────────┘
```

### 3
choose unique names for your reactive expressions that don't conflict with base R functions. For example:
```{r, eval=FALSE}
my_var <- reactive(df[[input$var]])
my_range <- reactive(range(my_var(), na.rm = TRUE))
```
Now 'my_var()' and 'my_range()' are custom names for your reactive expressions, avoiding the conflict with the base functions var() and range().

